The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-02-08 paper/paper.tex
more text and plots

\begin{abstract}
In this paper we present the results of the DESC 3x2pt tomography challenge,
which aims to compare strategies for optimizing the photometric binning required
for the main LSST 3x2pt analysis. This task is made particularly delicate in the
context of a metacalibrated lensing survey, as only the photometry from the
bands  included in the metacalibration process (riz and potentially g) can be
used to define this tomographic binning. Using a set of realistic simulations
including true galaxy redshifts and simulated photometry, the goal of the
challenge is to propose a bin assignment strategy that maximizes the overall
Figure of Merit of a 3x2pt analysis. This setting is idealized as it ignores
spectroscopic completeness  issues for the training sample, but complex enough
to address the main question of binning optimization. Based on the challenge
dataset, we review and compare the different methods that have been proposed by
participants. We find that even from this limited photometry information,
various methods are able to yield binning schemes that achieve high FoM scores.
\end{abstract}

@@

\subsubsection{Metric 1: Sigal-to-noise}
Our first metric is the total signal-to-noise ratio of the power spectrum derived from the assigned
$n_i(z)$ values:
\begin{equation}
    S = \mu^{T} C^{-1} \mu
\end{equation}
where $\mu$ is a stack of the theoretical predictions for the $C_\ell$ spectra for each tomographic 
bin, in turn, and $C$ a Gaussian estimaate of the covariance between them, as described in
\citet{wl-review} and summarized in \autoref{app:theory}.   We compute this metric for lensing alone, clustering alone, and the full 3x2pt combination.

@@

Metric 2 uses a figure of merit based on that presented by the Dark Energy Task Force \citep{detf}.  We 
use the inverse area of a Fisher Matrix ellipse, which approximates the size in two axes 
of the posterior PDF one would obtain on analysing the spectra:
\begin{align}
    F &= \left( \frac{\partial \mu}{\partial \theta} \right)^T C^{-1} \left( \frac{\partial \mu}{\partial \theta} \right), \\
    S &= \frac{1}{2 \pi \sqrt{\det{([F^{-1}]_{p_1, p_2})}}}
\end{align}
where $[F^{-1}]_{p_1, p_2}$ extracts the 2x2 matrix for two parameters.  We use both the original
DETF variant in which $p_1 = w_0, p_2 = w_a$, representing the constraining power on dark energy 
evolution, and a version in which $p_1 = \Omega_c$ and $p_2 = \sigma_8$, representing constraining
power on overall cosmic structure amplitude and its evolution.

@@

  Let ${\sf C}^{\rm group}_\ell$ be the matrix containing all auto- and cross-power spectra between members of a large set of galaxy samples (called ``groups'' here). We can compress this large set into a smaller set of samples (called ``bins'' here), by combining different groups. Let ${\sf A}$ be the assignment matrix determining these bins, such that $A_{\alpha,i}=1$ if group $i$ is assigned to bin $\alpha$, and 0 otherwise. In that case, the redshift distribution of bin $\alpha$ is given by $N_\alpha(z)=\sum_i A_{\alpha,i}n_i(z)$, where $n_i(z)$ is the redshift distribution of group $i$. Defining the normalized assignment matrix ${\sf B}$ as
  \begin{equation}
    B_{\alpha,i}=A_{\alpha,i}\frac{\int dz\,n_i(z)}{\sum_j A_{\alpha,j}\int dz\,n_j(z)},
  \end{equation}
  ${\sf C}^{\rm group}_\ell$ is related to the matrix of cross-power spectra between pairs of bins via:
  \begin{equation}
    {\sf C}^{\rm bin}_\ell={\sf B}\,{\sf C}^{\rm group}_\ell\,{\sf B}^T.
  \end{equation}

  The rationale behind the {\tt ComplexSOM} method is based on the observation that, while ${\sf C}^{\rm group}_\ell$ is a slow quantity to calculate for a large number of groups, ${\sf B}$ and therefore ${\sf C}^{\rm bin}_\ell$ are very fast. Thus, given an initial set of groups characterizing the distribution of the full sample in colour space, ${\sf C}^{\rm group}_\ell$ can be precomputed once, and used to find the optimal assignment matrix ${\sf B}$ that maximizes the figure of merit in Eq. {\bf reference to FoM equation}, which can be written in terms of ${\sf C}^{\rm bin}_\ell$ alone as
  \begin{equation}\label{eq:fom_tr}
    F_{\theta\theta'}=\sum_\ell f_{\rm sky}\frac{2\ell+1}{2}{\rm Tr}\left[\partial_\theta{\sf C}^{\rm bin}_\ell({\sf C}^{\rm bin}_\ell)^{-1}\partial_{\theta'}{\sf C}^{\rm bin}_\ell({\sf C}_\ell^{\rm bin})^{-1}\right].
  \end{equation}

@@

\begin{table*}[]
\begin{tabular}{|l|llll|llll|}
                & \multicolumn{4}{c|}{\textbf{riz}}      & \multicolumn{4}{c|}{\textbf{griz}}                                \\ \hline
\textbf{Method} & \textbf{3-bin} & \textbf{5-bin} & \textbf{7-bin} & \textbf{9-bin} & \textbf{3-bin} & \textbf{5-bin} & \textbf{7-bin} & \textbf{9-bin} \\ \hline
{\sc Autokeras\_LSTM } & 31.1 & 74.9    & 103.4    & --    & 44.1             & 67.5             & 122.2             & 98.4\\
{\sc CNN } & 27.1 & 50.8    & 76.7    & 103.3    & 30.5             & 57.7             & 95.4             & 122.4\\
{\sc ComplexSOM } & 38.0 & 52.1    & 94.4    & 101.6    & 34.9             & 45.0             & 91.6             & 100.3\\
{\sc ENSEMBLE1 } & 65.6 & 65.6    & 94.8    & --    & --             & --             & --             & --\\
{\sc funbins } & 36.8 & 82.5    & 122.1    & 141.8    & 42.1             & 100.4             & 142.5             & 167.2\\
{\sc GPzBinning } & 26.2 & 49.7    & 80.8    & 111.7    & 27.8             & 55.3             & 87.2             & 126.9\\
{\sc IBandOnly } & 38.0 & 50.0    & 54.4    & 57.3    & 38.0             & 50.0             & 54.4             & 57.3\\
{\sc JaxCNN } & 59.9 & 101.9    & 105.2    & --    & 79.7             & 125.2             & 150.0             & --\\
{\sc JaxResNet } & 73.7 & 111.1    & 131.6    & --    & 82.2             & 126.0             & --             & 161.5\\
{\sc LGBM } & 27.0 & 50.8    & 78.8    & 108.2    & 30.3             & 57.4             & 92.9             & 125.2\\
{\sc LSTM } & 26.7 & 51.1    & 81.4    & 103.6    & 30.2             & 57.1             & 95.9             & 126.9\\
{\sc mlpqna } & 39.3 & 64.7    & 93.2    & 121.8    & 42.8             & 72.2             & 109.0             & 133.7\\
{\sc myCombinedClassifiers } & 35.3 & 60.5    & 83.5    & 120.4    & 39.4             & 63.9             & 93.1             & 148.9\\
{\sc NeuralNetwork1 } & 76.3 & 117.6    & 135.8    & --    & 81.9             & 132.9             & 158.0             & --\\
{\sc NeuralNetwork2 } & 30.5 & 48.0    & 57.8    & 136.1    & 49.4             & 102.7             & 122.2             & 140.0\\
{\sc PCACluster } & 29.5 & 68.1    & 75.8    & --    & 50.1             & 72.7             & 90.8             & --\\
{\sc Random } & 1.2 & 1.2    & 1.2    & 1.2    & 1.2             & 1.2             & 1.2             & 1.2\\
{\sc RandomForest } & 39.5 & 65.2    & 93.2    & 118.5    & 43.0             & 72.8             & 110.1             & 136.5\\
{\sc SimpleSOM } & 39.5 & 59.9    & 77.9    & 98.5    & 42.2             & 73.2             & 108.0             & 134.8\\
{\sc TensorFlow\_FFNN } & 39.0 & 64.3    & 90.3    & 114.7    & 43.0             & 72.0             & 112.3             & 137.2\\
{\sc TCN } & 40.0 & 65.3    & 90.9    & 110.5    & 44.1             & 72.8             & 108.0             & 134.0\\
{\sc UTOPIA } & 39.0 & 63.7    & 90.8    & 112.2    & 43.1             & 74.0             & 112.8             & 139.3\\
{\sc ZotBin } & 64.8 & 106.4    & 121.8    & 135.3    & 77.6             & 120.0             & 141.8             & 154.7\\
{\sc ZotNet } & 73.6 & 111.2    & 131.8    & 145.9    & 83.7             & 128.5             & 150.1             & 167.2\\
\end{tabular}
\caption{INCOMPLETE, AND AUTO-GENERATED SO NO POINT EDITING! Values of the 3x2pt DETF figure-of-merit achieved by entrant methods on the 
CosmoDC2 part of the challenge.}
\label{tab:cosmodc2}
\end{table*}

@@

\section{Discussion}
\begin{itemize}
    \item Overall effectiveness of method classes
    \item Individual winner
\end{itemize}

-

\subsection{General outcomes}
It is clear from values above that fears about restricted photometry catastrophically limiting
the information needed for tomography are unfounded.  In both the CosmoDC2 and Buzzard analyses,
even the $riz$ bands alone are sufficient to split objects into nine reasonably separated
tomographic bins.  Once bins become this narrow the primary analysis concern will become the calibration of overall
bin $n(z)$ values, rather than initial tomography, so we consider this to be reassuring.

@@

\begin{itemize}
    \item spectroscopic incompleteness
\end{itemize}

\section{Conclusions}

@@

\section{Theory}\label{app:theory}
In our metrics, the power spectrum between two tomographic bins $i$ and $j$ is computed using either the Core Cosmology Library \citep{ccl} or the JAX Cosmology Library \citep{jax-cosmo} as:
\begin{equation}
    C^{ij}_\ell = \int_0^{\infty} \frac{q_i(\chi) q_j(\chi)}{\chi^2} P\left(\frac{\ell +\frac{1}{2}}{\chi}, \chi \right) \mathrm{d}\chi
\end{equation}
where $\chi = \chi(z)$ is the comoving distance and $P$ the non-linear matter power spectrum at
a fiducial cosmology.  The kernel functions $q_i(\chi)$ are different for the lensing and clustering samples:
\begin{align}
    q^{\mathrm{cluster}}_i(\chi) &= n_i(\chi)\\
    q^{\mathrm{lensing}}_i(\chi) &= \frac{3}{2}\Omega_m \left(\frac{\mathrm{H}_0}{c}\right)^2 \frac{\chi}{a(\chi)} \int_\chi^{\infty} \frac{\chi' - \chi}{\chi'} n_i(\chi')\,\,\mathrm{d}\chi'
\end{align}
where $n_i(\chi) = n_i(z) \frac{\mathrm{d}z}{\mathrm{d}\chi}$.

@@

\section{Complete results}

@@

\subsection{Guidance on caching \& batch processing}
Since the training process for the challenge could be slow for some algorithms, many entries
very reasonably cached trained models or other values for later use.  In some cases these
cached values were then incorrectly picked up by subsequent runs on new data sets, leading
to (at best) crashes and at worst silently poor scores.  We should have provided an explicit
caching mechanism for entrants to avoid such issues.

>>>>

\begin{abstract}
In this paper we present the results of the DESC 3x2pt tomography challenge,
which aims to compare strategies for optimizing the photometric binning required
for the main LSST 3x2pt analysis. This task is made particularly delicate in the
context of a metacalibrated lensing survey, as only the photometry from the
bands  included in the metacalibration process (riz and potentially g) can be
used to define this tomographic binning. Using a set of realistic simulations
including true galaxy redshifts and simulated photometry, the goal of the
challenge is to propose a bin assignment strategy that maximizes the overall
Figure of Merit of a 3x2pt analysis. This setting is idealized as it ignores
spectroscopic completeness  issues for the training sample, but complex enough
to address the main question of binning optimization. Based on the challenge
dataset, we review and compare the different methods that have been proposed by
participants. We find that even from this limited photometry information,
various methods are able to yield binning schemes that achieve high figure-of-merit scores.
\end{abstract}

@@

\subsubsection{Metric 1: Sigal-to-noise}
Our first metric is the total signal-to-noise ratio of the power spectrum derived from the assigned
$n_i(z)$ values:
\begin{equation}
    S = \mu^{T} C^{-1} \mu
\label{eq:snr}
\end{equation}
where $\mu$ is a stack of the theoretical predictions for the $C_\ell$ spectra for each tomographic 
bin, in turn, and $C$ a Gaussian estimaate of the covariance between them, as described in
\citet{wl-review} and summarized in \autoref{app:theory}.   We compute this metric for lensing alone, clustering alone, and the full 3x2pt combination.

@@

Metric 2 uses a figure of merit (FOM) based on that presented by the Dark Energy Task Force \citep{detf}.  We 
use the inverse area of a Fisher Matrix ellipse, which approximates the size in two axes 
of the posterior PDF one would obtain on analysing the spectra:
\begin{align}
    F &= \left( \frac{\partial \mu}{\partial \theta} \right)^T C^{-1} \left( \frac{\partial \mu}{\partial \theta} \right), \\
    S &= \frac{1}{2 \pi \sqrt{\det{([F^{-1}]_{p_1, p_2})}}}
\label{eq:fom}
\end{align}
where $[F^{-1}]_{p_1, p_2}$ extracts the 2x2 matrix for two parameters.  We use both the original
DETF variant in which $p_1 = w_0, p_2 = w_a$, representing the constraining power on dark energy 
evolution, and a version in which $p_1 = \Omega_c$ and $p_2 = \sigma_8$, representing constraining
power on overall cosmic structure amplitude and its evolution.

@@

Let ${\sf C}^{\rm group}_\ell$ be the matrix containing all auto- and
cross-power spectra between members of a large set of galaxy samples (called
``groups'' here). We can compress this large set into a smaller set of samples
(called ``bins'' here), by combining different groups. Let ${\sf A}$ be the
assignment matrix determining these bins, such that $A_{\alpha,i}=1$ if group
$i$ is assigned to bin $\alpha$, and 0 otherwise. In that case, the redshift
distribution of bin $\alpha$ is given by $N_\alpha(z)=\sum_i
A_{\alpha,i}n_i(z)$, where $n_i(z)$ is the redshift distribution of group $i$.

Defining the normalized assignment matrix ${\sf B}$ as
\begin{equation}
B_{\alpha,i}=A_{\alpha,i}\frac{\int dz\,n_i(z)}{\sum_j A_{\alpha,j}\int dz\,n_j(z)},
\end{equation}

${\sf C}^{\rm group}_\ell$ is related to the matrix of cross-power spectra
between pairs of bins via:
\begin{equation}
{\sf C}^{\rm bin}_\ell={\sf B}\,{\sf C}^{\rm group}_\ell\,{\sf B}^T.
\end{equation}

The rationale behind the {\tt ComplexSOM} method is based on the observation
that, while ${\sf C}^{\rm group}_\ell$ is a slow quantity to calculate for a
large number of groups, ${\sf B}$ and therefore ${\sf C}^{\rm bin}_\ell$ are
very fast. Thus, given an initial set of groups characterizing the
distribution of the full sample in colour space, ${\sf C}^{\rm group}_\ell$
can be precomputed once, and used to find the optimal assignment matrix ${\sf
B}$ that maximizes the figure of merit in Equation \ref{eq:fom},
which can be written in terms of ${\sf C}^{\rm bin}_\ell$ alone as

\begin{equation}\label{eq:fom_tr}
F_{\theta\theta'}=\sum_\ell f_{\rm sky}\frac{2\ell+1}{2}{\rm Tr}\left[\partial_\theta{\sf C}^{\rm bin}_\ell({\sf C}^{\rm bin}_\ell)^{-1}\partial_{\theta'}{\sf C}^{\rm bin}_\ell({\sf C}_\ell^{\rm bin})^{-1}\right].
\end{equation}

@@

\section{Overall results}
The methods described above were run on a data set, previously unseen by entrants but drawn
from the same underlying population, of size 8.6M objects for CosmoDC2 and 5.4M objects for Buzzard.
A complete suite of the metrics described in Section \ref{sec:metrics} was run on each of the two
for each method.  In total, each method was run on 16 scenarios, each combination of: griz vs riz,
Buzzard vs CosmoDC2, and 3,5,7, and 9 bins requested.  Nine metrics were calculated for each
scenario: clustering, lensing, and 3x2pt for each of the SNR metric (Equation \ref{eq:snr}, the $w_0-w_a$ 
DETF FOM, and the $\Omega_c - \sigma_8$ FOM (Equation \ref{eq:fom}).

The DETF results for each method are shown in Table \ref{tab:cosmodc2}.  Further results for other
metrics are shown in Appendix \ref{sec:complete}.  Missing entries occured in two ways.
The first, marked with an asterisk, is when a method did not run for the given scenario,
either due to memory overflow or taking an extremely long time.
The second, marked with a dash, is when a method ran, but generated at least one bin with an extremely small number
count, such that the spectrum could not be calculated.

\begin{table*}[]
\begin{tabular}{|l|llll|llll|}
                & \multicolumn{4}{c|}{\textbf{riz}}      & \multicolumn{4}{c|}{\textbf{griz}}                                \\ \hline
\textbf{Method} & \textbf{3-bin} & \textbf{5-bin} & \textbf{7-bin} & \textbf{9-bin} & \textbf{3-bin} & \textbf{5-bin} & \textbf{7-bin} & \textbf{9-bin} \\ \hline
{\sc Autokeras\_LSTM } & 31.1 & 74.9    & 103.4    & --    & 44.1             & 67.5             & 122.2             & 98.4\\
{\sc CNN } & 27.1 & 50.8    & 76.7    & 103.3    & 30.5             & 57.7             & 95.4             & 122.4\\
{\sc ComplexSOM } & 38.0 & 52.1    & 94.4    & 101.6    & 34.9             & 45.0             & 91.6             & 100.3\\
{\sc ENSEMBLE1 } & 65.6 & 65.6    & 94.8    & *    & *             & *             & *             & *\\
{\sc funbins } & 36.8 & 82.5    & 122.1    & 141.8    & 42.1             & 100.4             & 142.5             & 167.2\\
{\sc GPzBinning } & 26.2 & 49.7    & 80.8    & 111.7    & 27.8             & 55.3             & 87.2             & 126.9\\
{\sc IBandOnly } & 38.0 & 50.0    & 54.4    & 57.3    & 38.0             & 50.0             & 54.4             & 57.3\\
{\sc JaxCNN } & 59.9 & 101.9    & 105.2    & --    & 79.7             & 125.2             & 150.0             & --\\
{\sc JaxResNet } & 73.7 & 111.1    & 131.6    & --    & 82.2             & 126.0             & --             & 161.5\\
{\sc LGBM } & 27.0 & 50.8    & 78.8    & 108.2    & 30.3             & 57.4             & 92.9             & 125.2\\
{\sc LSTM } & 26.7 & 51.1    & 81.4    & 103.6    & 30.2             & 57.1             & 95.9             & 126.9\\
{\sc mlpqna } & 39.3 & 64.7    & 93.2    & 121.8    & 42.8             & 72.2             & 109.0             & 133.7\\
{\sc myCombinedClassifiers } & 35.3 & 60.5    & 83.5    & 120.4    & 39.4             & 63.9             & 93.1             & 148.9\\
{\sc NeuralNetwork1 } & 76.3 & 117.6    & 135.8    & 109.9    & 81.9             & 132.9             & 158.0             & 96.9\\
{\sc NeuralNetwork2 } & 30.5 & 48.0    & 57.8    & 136.1    & 49.4             & 102.7             & 122.2             & 140.0\\
{\sc PCACluster } & 29.5 & 68.1    & 75.8    & *    & 50.1             & 72.7             & 90.8             & *\\
{\sc Random } & 1.2 & 1.2    & 1.2    & 1.2    & 1.2             & 1.2             & 1.2             & 1.2\\
{\sc RandomForest } & 39.5 & 65.2    & 93.2    & 118.5    & 43.0             & 72.8             & 110.1             & 136.5\\
{\sc SimpleSOM } & 39.5 & 59.9    & 77.9    & 98.5    & 42.2             & 73.2             & 108.0             & 134.8\\
{\sc TensorFlow\_FFNN } & 39.0 & 64.3    & 90.3    & 114.7    & 43.0             & 72.0             & 112.3             & 137.2\\
{\sc TCN } & 40.0 & 65.3    & 90.9    & 110.5    & 44.1             & 72.8             & 108.0             & 134.0\\
{\sc UTOPIA } & 39.0 & 63.7    & 90.8    & 112.2    & 43.1             & 74.0             & 112.8             & 139.3\\
{\sc ZotBin } & 64.8 & 106.4    & 121.8    & 135.3    & 77.6             & 120.0             & 141.8             & 154.7\\
{\sc ZotNet } & 73.6 & 111.2    & 131.8    & 145.9    & 83.7             & 128.5             & 150.1             & 167.2\\
\end{tabular}
\caption{INCOMPLETE, AND AUTO-GENERATED SO NO POINT EDITING! Values of the 3x2pt DETF figure-of-merit achieved by entrant methods on the 
CosmoDC2 part of the challenge.}
\label{tab:cosmodc2}
\end{table*}

\subsection{Metric comparisons}
Figure \ref{fig:metrics} shows a comparison of some of the different metrics used in the challenge.

\begin{figure}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/metric_comparisons.pdf}
\caption{A comparison of the metrics used in our challenge. The x-axis is shared, and shows
the 3x2pt $w_0 - w_a$ (DETF) figure of merit on the CosmoDC2 data set for all methods, 
with colours labelling the number
of bins used.  Each of the panels shows a metric which is the same except for a single change, 
which is labelled on its y-axis.  For example, the top panel still shows the 3x2pt $w_0 - w_a$ (DETF) figure of merit,
but for the Buzzard data set.}
\label{fig:metrics}
\end{figure}

\subsection{Impact of losing g-band}
Figure \ref{fig:loss} shows the ratio of the FOM between methods using the griz and the same method
using the riz.  Each point represents one method with a specific number of bins, indicated by colour.
For lower scoring methods and for smaller numbers of bins there is more scatter in the ratio,
but for the highest scoring algorithms and configurations the loss when losing g-band is a little
more stable, at around 10--15\%.

\begin{figure*}
\includegraphics[width=0.9\linewidth]{results/g_band_loss.pdf}
\caption{The degradation in constraining power over all methods
 when comparing them on methods including and excluding
the g-band, in terms of the ratio of the $w_0-w-a$ figure of merit.  The left-hand panel shows
results for the CosmoDC2 scenarios, and the right-hand panel for the Buzzard scenarios.  Colours
indicate the number of bins used in the analysis.}
\label{fig:loss}
\end{figure*}

\subsection{Trained edges vs fixed edges}

Some of the methods in the challenge accepted target bin edges as an input to their algorithms,
and then used classifiers to assign objects to those bins.  Other methods optimized the values
of bin edges themselves.

@@

\section{Discussion}
It is clear from values above that fears about restricted photometry catastrophically limiting
the information needed for tomography are unfounded.  In both the CosmoDC2 and Buzzard analyses,
even the $riz$ bands alone are sufficient to split objects into nine reasonably separated
tomographic bins.  Once bins become this narrow the primary analysis concern will become the calibration of overall
bin $n(z)$ values, rather than initial tomography, so we consider this to be reassuring.

@@

\begin{itemize}
    \item spectroscopic incompleteness / unrepresentativeness
    \item data set volume
    \item comparison of optimal choices in different science cases
\end{itemize}

@@

\section{Theory}\label{app:theory}

In our metrics, the power spectrum between two tomographic bins $i$ and $j$ is
computed using either the Core Cosmology Library \citep{ccl} or the JAX
Cosmology Library \citep{jax-cosmo} as:

\begin{equation}
    C^{ij}_\ell = \int_0^{\infty} \frac{q_i(\chi) q_j(\chi)}{\chi^2} P\left(\frac{\ell +\frac{1}{2}}{\chi}, \chi \right) \mathrm{d}\chi
\end{equation}
where $\chi = \chi(z)$ is the comoving distance and $P$ the non-linear matter power spectrum at
a fiducial cosmology.  The kernel functions $q_i(\chi)$ are different for the lensing and clustering samples:
\begin{align}
    q^{\mathrm{cluster}}_i(\chi) &= n_i(\chi)\\
    q^{\mathrm{lensing}}_i(\chi) &= \frac{3}{2}\Omega_m \left(\frac{\mathrm{H}_0}{c}\right)^2 \frac{\chi}{a(\chi)} \int_\chi^{\infty} \frac{\chi' - \chi}{\chi'} n_i(\chi')\,\,\mathrm{d}\chi'
\end{align}
where $n_i(\chi) = n_i(z) \frac{\mathrm{d}z}{\mathrm{d}\chi}$.

@@

\section{Complete results}
\label{sec:complete}

@@

\subsection{Guidance on caching \& batch processing}
Since the training process for the challenge could be slow for some algorithms, many entries
(very reasonably) cached trained models or other values for later use.  In some cases these
cached values were then incorrectly picked up by subsequent runs on new data sets, leading
to (at best) crashes and at worst silently poor scores.  We should have provided an explicit
caching mechanism for entrants to avoid such issues.
